Denotational Semantics of General Payment Primitives, and Its Payment System

### 2022-09-27 packages/spec-haskell/yellowpaper/Paper.tex
added Payment System Solvency subsection

>>>>

While money distribution does not assign meaning to the range of monetary values, in real world applications, negative
values can have special meanings. In the following analysis, we call any money unit that has a negative monetary value
insolvent.

The detailed analysis of these solvency models are out of scope for this paper.

\paragraph{Buffer Based Solvency Treatment}

In a nondeterministic execution environment, we cannot determine when any financial contract will actually be
executed. That means, there is always a chance a monetary unit could reach negative monetary value.

To mitigate this uncertainty, a concept called buffer is introduced. A buffer has a monetary value which is set aside in a solvency conditional financial contract, such that if a solvency
condition arises, the buffer maybe drawn to cover the loss introduced by the nondeterministic timing of the execution.

\paragraph{Deterministic Solvency Treatment}

Since \textit{fcNext} returns what is the next financial contract executable at a specific time, this deterministic
property eliminates the need for the buffer.

But it introduces a different type of systemic risk, that is denial-of-service, since the system cannot advance the
system time until all next executable contracts are executed.
